Enabling Ambient Backscatter \\Using a Low-Cost Software Defined Radio

### 2017-04-07 paper.tex

\subsection{Signal Strength Variation in Space}
\begin{figure}[h]
	\centering
	\begin{minipage}{0.49\columnwidth}
	\includegraphics[width=\columnwidth]{./fig/626mhz_raw}
	\end{minipage}
	\hfill
	\begin{minipage}{0.49\columnwidth}
	\includegraphics[width=\columnwidth]{./fig/626mhz_filtered}
	\end{minipage}
	\caption{Spectrum of the TV signal. Left: Raw spectrum of the TV signal with \ensuremath{f_{\text{center}}=\text{626 Mhz}}. Left: Smoothed spectrum, normalized to maximum average measured in decibel with average shown as red line.}
	\label{fig:tv_record} 
\end{figure}

We have used the \textit{RTL-SDR} to observe the space variations of the
signal strength. \textit{Octave} scripts have been written to aid in
this purpose. These scripts are available online under
\url{https://github.com/s3xm3x/RTLSDRspecAn}. The scripts perform a
frequency sweep through the desired band. The obtained samples are then
transferred from the time domain to the frequency domain using a fast
fourier transformation (FFT).

>>>>

\subsection{Signal Strength Variation in Space}
\begin{figure}[h]
	\centering
	\begin{minipage}{0.49\columnwidth}
	\includegraphics[width=\columnwidth]{./fig/626mhz_raw}
	\end{minipage}
	\hfill
	\begin{minipage}{0.49\columnwidth}
	\includegraphics[width=\columnwidth]{./fig/626mhz_filtered}
	\end{minipage}
	\caption{Spectrum of the TV signal. Left: Raw spectrum of the TV signal with \ensuremath{f_{\text{center}}=\text{626 Mhz}}. Right: Smoothed spectrum, normalized to maximum average measured in decibel with average shown as red line.}
	\label{fig:tv_record} 
\end{figure}

We have used the \textit{RTL-SDR} to observe the space variations of the
signal strength. \textit{Octave} scripts have been written to aid in
this purpose. These scripts are available under \cite{s3xm3x_RTLSDRSpecAn}. The scripts perform a
frequency sweep through the desired band. The obtained samples are then
transferred from the time domain to the frequency domain using a fast
fourier transformation (FFT).
